---
title: "question 4.36"
format: html
editor: visual
---

```{r}
library(tidyverse)
snowrates <- tibble(snow_fall = c(45, 59, 82, 80, 71, 60, 55, 69, 79, 95),
                  unemployment_rates = c(4.9, 5.6, 8.5, 7.7, 7.1, 6.1, 5.8, 7.1, 7.6, 9.7),
                 )

```

a\) Make a scatter plot of unemployment rates vs. snowfall. what relationship is indicated by the scatter plot?

```{r}
ggplot(snowrates) +
  geom_point(mapping = aes(x=snow_fall, y= unemployment_rates))
```

There appears to be a positive linear relationship between snow fall and unemployment rates.

b\) Calculate the correlation coefficient. Is there a strong linear relationship between snowfall and unemployment?

```{r}
cor(snowrates)
```

with a value of 0.98, there appears to be a very strong relationship.

c\) Does this relationship mean that Amherst annual snowfall influences the national unemployment rates or vice versa?

No. While the two events have high correlation, correlation is no causation, so we should preform further inference before stating any such influences.
